\documentclass[9pt, a4paper]{extarticle}

\usepackage[left=1.91cm,right=1.91cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{mathrsfs}
\usepackage[ruled,lined,linesnumbered]{algorithm2e}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{diagbox}
\usepackage{xspace}
%\usepackage{subfigure}
%\usepackage{soul}
\usepackage{color}
\usepackage{CJK}
\usepackage{todonotes}
%\usepackage[colorlinks,linkcolor=black,
%anchorcolor=black,citecolor=blue]{hyperref}

%\def\RCKNNG{\mbox{RC-$k$NNG}\xspace}
\def\OUR{\mbox{Ours}\xspace}
\def\PRESEG{\mbox{PreSeg}\xspace}

%-------------------------- 自定义命令 --------------------------
\newcommand{\TODO}[1]{\textcolor{red}{#1}}  % 字体显示为红色，表达将要做的（但还未做）的事
\newcommand{\DONE}{\textcolor{red}{\bf DONE}} % 表示已完成
\newcommand{\DONING}{\textcolor{blue}{\bf DONING}} % 表示完成了一部分
\newcommand{\NDR}{\textcolor{red}{\textbf{[Need Review]}}} % need review

\setlength{\parskip}{3ex}   % 行间距
\setlength{\parindent}{0pt}   % 首先缩进

% \renewcommand{\theenumi}{\bf {\arabic{enumi})}}  % enumerate, itemize, description内部的标识

\newcommand{\tinytodo}[2][]
{\todo[caption={#2}, size=\small, #1]{\renewcommand{\baselinestretch}{0.5}\selectfont#2\par}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{CJK*}{GBK}{song}

\title{针对浏览式草图造型的按需部件建议技术 \\
Exploratory Sketch-Based Modeling with On-Demand Part Customization}
\author{Xuekun Guo}
\date{2016.04.25}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{摘要}
在基于部件组合的创造力支持的造型技术中，从数据库内实时提取可添加到当前模型的部件是最具挑战的问题之一。
我们提出一种基于草图的按需部件建议方法。
用户输入草图表达设计概念，我们的方法基于草图生成三维代理部件，并基于代理部件从数据库内提取一系列候选部件，做为提示建议给用户。
候选部件通过局部匹配方法实时地从数据库模型内搜索得到。
与以前的方法不同，我们的方法不依赖预分割的三维模型数据库，向用户建议任意个性化的部件，极大地扩展了造型空间。
实验表明我们的方法简单而且直观，允许普通用户快捷方便地造型有意思的模型。

创造力支持的造型；草图式造型；局部匹配；实时分割；

Suggesting inspiring parts on-the-fly from collections of 3D models is a challenge in assembly-based creative modeling.
We present a sketch-based on-demand part suggestion method for creating shapes using sketches.
After a user draws a simple abstract sketch which depicts his/her intention,
our method creates a 3D proxy based on the input sketch as a search key to retrieve a list of candidate parts,
each of which is segmented on-the-fly from the 3D models in the input database using partial matching.
In contrast to prior work, our proxy-to-design approach can customize arbitrary parts from input models and does not rely on predefined parts,
which significantly broadens the design space.
Experimental results indicate that our approach provides an intuitive and easy means to create novel designs,
and allows novices to generate interesting models that are otherwise difficult to attain.

Creative modeling; Sketch-based modeling; Partial matching; on-the-fly segmentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Tex/Intro.tex}
%\input{Tex/Related.tex}
%\input{Tex/Over.tex}
%\input{Tex/Index.tex}
%\input{Tex/Retr.tex}
%\input{Tex/Refine.tex}
%\input{Tex/Res.tex}
%\input{Tex/Conc.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{alpha}
\bibliography{Bib}
\end{CJK*}
\end{document} 